paper1-INTERACT-analysis

### 2024-09-16 paper1-INTERACT-analysis.Rmd
Added additional calculations

>>>>

Valid days of data per person -- wave 1
```{r}
sd_valid_per_person<-sd_valid %>% group_by(interact_id,wave_id) %>% mutate(rows=length(interact_id)) %>% 
                     dplyr::select(interact_id,rows) %>% distinct()
mean(sd_valid_per_person[sd_valid_per_person$wave_id=="wave 1",]$rows)
sd(sd_valid_per_person[sd_valid_per_person$wave_id=="wave 1",]$rows)
```

Valid days of data per person -- wave 2
```{r}
mean(sd_valid_per_person[sd_valid_per_person$wave_id=="wave 2",]$rows)
sd(sd_valid_per_person[sd_valid_per_person$wave_id=="wave 2",]$rows)
```
